### 2020-04-12 Thesis-Chapter2-Background.tex
Work on EA regulations section

% FIXME: Kristen doesn't like the wording; also remove word "electronic"?
Electronic encryption's dual role as enabler of strong privacy and cornerstone of computer security may be the central
conflict in the EA debate. Those who focus on its role in privacy object to its absolute power. Those who focus on its
role in security rely on its absolute power.

@@

@@

\lawsstart
    \law{1789}{\acf{AWA}}{congress_1789}{}

    \law{1791}{Bill of Rights: Amendments I, IV, and V}{madison_1791}{}

@@

Established export controls over strong encryption techniques introduced ITAR (International Traffic in Arms
Regulations) \cite{kehl_right_2015}

@@

    \law{1978}{\acf{FISA}}{rodino_1978}{}

% (FISA has been the subject of frequent FBI abuse: \cite{shamsi_2011} \cite{tucker_2020})
% (the FBI almost lost some provisions; follow up on https://apnews.com/110ff653e98478da66765897dde3d613,
%     https://www.washingtontimes.com/news/2020/mar/15/adam-schiff-fisa-reform-intervention-protects-fbi-/,
%     https://saraacarter.com/fisa-senate-passes-measure-extending-surveillance-powers-abuses-not-addressed/)

@@

% There are several types of approaches:
% - Allow strong encryption (anyone with the users' private keys can see it)
% - Disallow encryption (anyone can see it)
% - Make encryption sufficiently weak, e.g. limit key length (anyone with enough CPU can see it)
% - Require use of backdoored algorithms, security via obscurity (anyone with the secret knowledge can see it)
% - Allow any encryption, just be able to provide keys (anyone with the extra keys can see it)
%   - Store extra in gov't DBs, in corporate DBs, in third-party DBs, on blockchain, in secure HW on device
%   - Split the key and store it multiple places
% - Use some alternative path
%   - Coerced passwords, finding unencrypted copies, seizing devices while unlocked, lawful hacking

>>>>

% FIXME: Kristen doesn't like the wording; also remove word "electronic"?
Encryption's dual role as enabler of strong privacy and cornerstone of computer security may be the central conflict in
the EA debate. Those who focus on its role in privacy object to its absolute power. Those who focus on its role in
security rely on its absolute power.

@@

The following sections list laws which directly or indirectly affect use encryption. \Ac{EA} is an international
problem, as digital technology has little respect for borders. This paper is U.S.-focused, but briefly touches on the
regulatory environment of other countries.

@@

\lawsstart
    \law{1789}{\acf{AWA}}{congress_1789}{

A short law designed to grant federal courts the right to ``issue all writs necessary or appropriate in aid of their
respective jurisdictions and agreeable to the usages and principles of law,'' creating a legal framework for providing
data to law enforcement. The \acs{AWA} was famously cited in the Apple vs. FBI case, though its applicability to \ac{EA}
in general is unsettled \cite{matyas_incommensurability_2018}.

    \law{1791}{Bill of Rights: Amendments I, IV, and V}{madison_1791}{

The most frequently cited constitutional amendments in the \ac{EA} debate. I: freedom of speech; IV: security against
unreasonable searches and seizures and requirements for warrants; V: right against self-incrimination.

@@

Expanded arms export controls and created the \ac{ITAR} regulations framework. Encryption products were classified as
arms and subjected to export controls \cite{kehl_right_2015}.

@@

    \law{1978}{\acf{FISA}}{rodino_1978}{

Allows the executive branch ``to authorize electronic surveillance for foreign intelligence purposes without a court
order, in some circumstances.'' \acs{FISA} applications take place in secret, and may be conducted against U.S. citizens
if foreign intelligence is the ``primary purpose'' \cite{shamsi_2011}. \acs{FISA} has been the subject of frequent FBI
abuse \cite{shamsi_2011} \cite{tucker_2020}.

% (the FBI almost lost some provisions; follow up on https://apnews.com/110ff653e98478da66765897dde3d613,
%     https://www.washingtontimes.com/news/2020/mar/15/adam-schiff-fisa-reform-intervention-protects-fbi-/,
%     https://saraacarter.com/fisa-senate-passes-measure-extending-surveillance-powers-abuses-not-addressed/)

@@

% There are several types of approaches:
% TODO: after defense, create table of these and reference it in \prop lists below
% - Allow strong encryption (anyone with the users' private keys can see it)
% - Disallow encryption (anyone can see it)
% - Make encryption sufficiently weak, e.g. limit key length (anyone with enough CPU can see it)
% - Require use of backdoored algorithms, security via obscurity (anyone with the secret knowledge can see it)
% - Allow any encryption, just be able to provide keys (anyone with the extra keys can see it)
%   - Store extra in gov't DBs, in corporate DBs, in third-party DBs, on blockchain, in secure HW on device
%   - Split the key and store it multiple places
% - Use some alternative path
%   - Coerced passwords, finding unencrypted copies, seizing devices while unlocked, lawful hacking
